A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-01-29 paper.tex
tried to explain treeformula's better

The CEGAR loop depends on the ability to guess candidate partial strategies in
\textsc{findCandidate}. For this purpose we use the heuristic that a partial
strategy may be winning if for each \textsc{outcome} in the tree there exists a
play of controller and environment actions that is winning for the current
player. We can formulate this heuristic as a SAT query, which is constructed
recursively by $\textsc{treeFormula}$ ($\textsc{\textoverline{treeFormula}}$)
in Algorithm~\ref{alg:treeFormula}. The tree is first extended to the maximum
bound with \emph{unfixed} actions that allow existential choice by the SAT
solver. Then each game round in the tree is encoded in CNF by making copies of
the transition relation along with the winning condition of the current player.

The heuristic is based on the observation that for many synthesis problems in
the real world the final implementation will cooperate with its environment.
The existential search of the SAT solver simulates cooperation between the two
players.

>>>>

The CEGAR loop depends on the ability to guess candidate partial strategies in
\textsc{findCandidate}. For this purpose we use the heuristic that a partial
strategy may be winning if each \textsc{outcome} of the strategy can be extended to a
run of the game that is winning for the current player.  Clearly, if such a partial 
strategy does not exist then no winning partial strategy can exist for the abstract 
game tree.  
We can formulate this heuristic as a SAT query, which is constructed
recursively by $\textsc{treeFormula}$ (for the controller) or $\textsc{\textoverline{treeFormula}}$
(for the environment) in Algorithm~\ref{alg:treeFormula}. The tree is first extended to the maximum
bound with edges that are labeled with arbitrary opponent actions (Algorithm~\ref{alg:bounded}, line 14) as shown in Figure~\ref{}.  
Then each edge in the tree is encoded in CNF by making copies of the transition relation along with the 
winning condition.

%The heuristic is based on the observation that for many synthesis problems in
%the real world the final implementation will cooperate with its environment.
%The existential search of the SAT solver simulates cooperation between the two
%players.
